---
title: "Airbnb Dashboard"
author: "Seo Yoojin"
output: 
  flexdashboard::flex_dashboard:
    theme: journal
    orientation: rows
    vertical_layout: scroll
    
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(duckdb)
library(plotly)
library(glue)
library(scales)
library(leaflet)
library(ggthemes)
library(reactable)

library(tidyverse)
library(lubridate)
library(padr)
library(duckdb)
library(DBI)
library(shiny)
library(leaflet.extras)
library(shinyWidgets)
```

```{r}
con1 <- dbConnect(duckdb())
df_host_new <- read_csv("df_host_new.csv",col_types = readr::cols(
    X1 = readr::col_double(),  
    x = readr::col_double()))
df_new_listing <- read_csv("df_new_listing.csv",col_types = readr::cols(
    X1 = readr::col_double(),  
    x = readr::col_double()))
duckdb_register(con1,"host_info",df_host_new)
duckdb_register(con1,"listing",df_new_listing)

# Number of Listing ---------
n_listing <- dbGetQuery(con1, 
                        "SELECT COUNT(*) as freq 
                   FROM listing")%>% 
    pull(freq)

# Number of Host -----
n_host <- dbGetQuery(con1, 
                     "SELECT COUNT(*) as freq 
                   FROM host_info"
)%>% 
    pull(freq)

# Number of Review ----------
n_review <- dbGetQuery(con1, 
                       "SELECT SUM(number_of_reviews) as freq 
                   FROM listing"
)%>% 
    pull(freq)

# Data for Map --------
host_info_map <- dbGetQuery(con1, "SELECT name, listing_url, latitude, longitude, price, review_scores_rating, number_of_reviews, listing.host_id, host_info.host_name FROM listing
LEFT JOIN host_info ON listing.host_id = host_info.host_id")%>% replace_na(list(description = "No Description", review_scores_rating = "No Rating Yet"
))

# Get different room type
df_room_type <- dbGetQuery(con1, 
                   "SELECT DISTINCT room_type 
                  FROM listing")

# Get different neighbourhood
df_neighbour <- dbGetQuery(con1, 
                   "SELECT DISTINCT neighbourhood_cleansed
                   FROM listing")

# Number of Superhost
n_superhost <- dbGetQuery(con1,
                   "SELECT COUNT(*) as frequency
                   FROM host_info
                   WHERE host_is_superhost =1 ") 
                 
# Number of Verified Host
n_host_verified <- dbGetQuery(con1,
                   "SELECT COUNT(*) as frequency
                   FROM host_info
                   WHERE host_identity_verified =1 "
                   
)

# Number of Non-Verified Host
n_host_non_verified <- dbGetQuery(con1,
                   "SELECT COUNT(*) as frequency
                   FROM host_info
                   WHERE NOT host_identity_verified =1 "
                   
)
```
Airbnb Bangkok, Thailand {.sidebar}
=====================================
### About this dashboard 

Airbnb, Inc. is an American company that operates an online marketplace for lodging, primarily homestays for vacation rentals, and tourism activities.On this dashboard you can explore information regarding the host and room listings available in Bangkok, Central Thailand, Thailand. All data is sourced from publicly available information from http://insideairbnb.com/get-the-data.html the Airbnb site. All monetary values are presented in local currency (Thailand Baht or THB)."


Overview
=====================================  
Row {data-height=200}
-----------------------------------------------------------------------
### NUMBER OF ROOM LISTING
```{r}
valueBox(value=number(n_listing,big.mark=","), 
         icon = "fa-bed", 
         caption = "Number of Room Listing",
         color = 'success')
```

### NUMBER OF HOST
```{r}

valueBox(value=number(n_host,big.mark=","), 
         icon = "fa-user-alt", 
         caption = "Number of Host",
         color = "#41D0E6")
```

### TOTAL REVIEWS
```{r}
valueBox(value=number(n_review,big.mark=","), 
         icon = "fa-comment", 
         caption = "Total Reviews",
         color = "#83E641")
```

Row {data-height=800}
-----------------------------------------------------------------------

### Map of Bangkok, Thailand
```{r}
popup <- paste0("<b>", host_info_map$name, "</b><br>",
                        "Host Name: <b>", host_info_map$host_name, "</b><br>",
                        "Price: THB <b>", number(host_info_map$price, big.mark = ","), "</b><br>",
                        "Review Scores Rating: <b>", host_info_map$review_scores_rating , "</b><br>",
                        "Number of Reviews: <b>", number(host_info_map$number_of_reviews, big.mark = ","), "</b><br>",
                        "<a href=", host_info_map$listing_url, " target='_blank'> Click for more info</a>"
        )

leaflet(data = host_info_map) %>% 
            addTiles() %>% 
            addMarkers(lat = ~latitude, 
                       lng = ~longitude,
                       popup = popup,
                       clusterOptions = markerClusterOptions())
```

Room Listing
=====================================  
Row {data-height=100}
-----------------------------------------------------------------------
### Different Room Type on Airbnb
Airbnb hosts can list entire homes/apartments, private or shared rooms.  Airbnb provides detailed guides (https://www.airbnb.com/help/topic/1424/preparing-to-host) on how hosts could set up their places.

Row {data-height=200}
-----------------------------------------------------------------------
###
```{r}
selectInput(inputId = "select_room", label = "Select Room Type", choices = c("All", df_room_type$room_type ))
```   

###
```{r}
selectInput(inputId = "select_cat", label = "Select Category", 
                                                                  choices = list("Price" = "price",
                                                                                 "Overall Rating" = "review_scores_rating",
                                                                                 "Number of Review" = "number_of_reviews"
                                                                  )
                                                      )
```   

### 
```{r}                                                    
selectInput(inputId = "select_neighbour", label = "Select Neighbourhood",
                                                              choices = c("All Region", sort(df_neighbour$neighbourhood_cleansed)),
                                                              multiple = T,
                                                              selected = "All Region"
                                                              )
```    

Row {.tabset data-height=500}
-----------------------------------------------------------------------
### Room Type by Number of Listing
```{r}
plotlyOutput("listing_room_type", width = 800)

```

### Top 10 Room 
```{r}
plotlyOutput("listing_top", height = 500)
```

### Commonly provided ammenities
```{r}
 plotlyOutput("listing_amenities")
```

```{r}
 # Top Room Type ------------
    output$listing_room_type <- renderPlotly({
        
        out_db <- dbGetQuery(con1,
                           "SELECT room_type, COUNT(*) as frequency, AVG(price) as mean_price
                           FROM listing
                           GROUP BY room_type
                           ORDER BY COUNT(*) DESC"
                           )%>% mutate(room_type = ifelse(room_type == "Entire home/apt", "Entire home/apartment", room_type))
        

        plot_ly(data = out_db, 
                labels = ~room_type, values = ~frequency) %>% 
            add_pie(hole = 0.6, 
                    hovertemplate = paste0("<b>", out_db$room_type, "</b><br>",
                                           "Number of Listing: ", number(out_db$frequency, big.mark = ','), "<br>",
                                           "Average Price/Night : ",  number(out_db$mean_price, big.mark = ',', prefix = 'THB '),
                                           "<extra></extra>"
                                           )
                    ) %>% 
            layout(title = "<b>Room Type by Number of Listing</b>") %>% 
            config(displayModeBar = F)
        
    })
    
    
    
    # Change input Tab 2--------------
    ## If user select all region, other choices will be omitted
    
    observeEvent(input$select_neighbour, {
        
        if (length(input$select_neighbour) > 1 & "All Region" == input$select_neighbour[1]) {
            
            input_area <- input$select_neighbour[ input$select_neighbour != "All Region"]
            
            updateSelectInput(session,
                              inputId = "select_neighbour", label = "Select Neighbourhood",
                              choices = c("All Region", sort(df_neighbour$neighbourhood_cleansed)),
                              selected = input_area
            )
        } else if(length(input$select_neighbour) > 1 & "All Region" != input$select_neighbour[1] & "All Region" %in% input$select_neighbour){ # All region is selected but not as the first one
            
            updateSelectInput(session,
                              inputId = "select_neighbour", label = "Select Neighbourhood",
                              choices = c("All Region", sort(df_neighbour$neighbourhood_cleansed)),
                              selected = "All Region"
            )
            
        }})
      
      output$listing_top <- renderPlotly({
        
        # User select all for select room type and select neighbourhood
        if (input$select_room == "All" & ("All Region" %in% input$select_neighbour | length(input$select_neighbour) ==0)) {
            query <- paste0("SELECT name, AVG(price) as price, AVG(review_scores_rating) as review_scores_rating, AVG(number_of_reviews) as number_of_reviews, host_info.host_name
                           FROM listing
                           LEFT JOIN host_info
                           ON listing.host_id = host_info.host_id
                           WHERE review_scores_rating IS NOT NULL AND number_of_reviews > 10
                           GROUP BY name, host_info.host_name
                           ORDER BY ", input$select_cat ," DESC
                           LIMIT 10
                            ")
        } else if(input$select_room != "All" & ("All Region" %in% input$select_neighbour | length(input$select_neighbour) ==0)) { # user select all region but specific room type
            
            query <- paste0("SELECT name, AVG(price) as price, AVG(review_scores_rating) as review_scores_rating, AVG(number_of_reviews) as number_of_reviews, host_info.host_name
                           FROM listing
                           LEFT JOIN host_info
                           ON listing.host_id = host_info.host_id
                           WHERE room_type = '", input$select_room,"' AND review_scores_rating IS NOT NULL AND number_of_reviews > 10
                           GROUP BY name, host_info.host_name
                           ORDER BY ", input$select_cat ," DESC
                           LIMIT 10
                            ")
        } else if(input$select_room == "All" & !("All Region" %in% input$select_neighbour)){ # User select all room type but specific neighbourhood 
            
            input_area <- input$select_neighbour %>%  
                paste0("'", ., "'") %>% 
                paste(collapse = ", ")
            
            query <- paste0("SELECT name, AVG(price) as price, AVG(review_scores_rating) as review_scores_rating, AVG(number_of_reviews) as number_of_reviews, host_info.host_name
                           FROM listing
                           LEFT JOIN host_info
                           ON listing.host_id = host_info.host_id
                           WHERE neighbourhood_cleansed IN(",  input_area ,") AND review_scores_rating IS NOT NULL AND number_of_reviews > 10
                           GROUP BY name, host_info.host_name
                           ORDER BY ", input$select_cat ," DESC
                           LIMIT 10
                            ")
            
        } else {
            
            input_area <- df_neighbour$neighbourhood_cleansed %>% 
                head(3) %>% 
                paste0("'", ., "'") %>% 
                paste(collapse = ", ")
            
            query <- paste0("SELECT name, AVG(price) as price, AVG(review_scores_rating) as review_scores_rating, AVG(number_of_reviews) as number_of_reviews, host_info.host_name
                           FROM listing
                           LEFT JOIN host_info
                           ON listing.host_id = host_info.host_id
                           WHERE room_type = '", input$select_room,"' AND neighbourhood_cleansed IN(",  input_area ,") AND review_scores_rating IS NOT NULL AND number_of_reviews > 10
                           GROUP BY name, host_info.host_name
                           ORDER BY ", input$select_cat ," DESC
                           LIMIT 10
                            ")
            
        }

        out_db <- dbGetQuery(con1, query)
        
        
        clean_input <- input$select_cat %>% 
            str_replace_all("_", " ") %>% 
            str_to_title()
            
        out_db <- out_db %>% 
            mutate(popup = glue("<b>{name}</b>
                                Host: {host_name}
                                Price: THB {number(price, big.mark = ',')}
                                Rating: {round(review_scores_rating, 3)}
                                Number of Reviews: {number(number_of_reviews, big.mark = ',')}
                                ")) 
        
        p <- out_db %>% 
            ggplot(aes(x = out_db[, input$select_cat], 
                       y = name %>% reorder(out_db[ , input$select_cat]),
                       fill = out_db[, input$select_cat],
                       text = popup
                       )
                   ) +
            geom_col(width = 0.75) +
            scale_x_continuous(labels = number_format(big.mark = ",")) +
            scale_fill_gradient(low = "dodgerblue4", high = "skyblue") +
            labs(x = clean_input,
                 y = NULL,
                 title = "Top 10 Room Listing"
                 ) +
            theme_pander() +
            theme(axis.text.y = element_text(size = 8)
                  )
        
        ggplotly(p, tooltip = "text") %>% 
            config(displayModeBar = F) %>% 
            hide_colorbar()
        
    })
    
    # Top Amenities -----------
    output$listing_amenities <- renderPlotly({
        
        if (input$select_room == "All" & ("All Region" %in% input$select_neighbour | length(input$select_neighbour) ==0)) {
            query <- "SELECT amenities FROM listing"
        } else if (input$select_room != "All" & ("All Region" %in% input$select_neighbour | length(input$select_neighbour) ==0)){
            query <- paste0("SELECT amenities FROM listing
                             WHERE room_type = '", input$select_room,"'"
                            )
        } else if(input$select_room == "All" & !("All Region" %in% input$select_neighbour)){
            input_area <- input$select_neighbour %>%  
                paste0("'", ., "'") %>% 
                paste(collapse = ", ")
            
            query <- paste0("SELECT amenities FROM listing
                             WHERE neighbourhood_cleansed IN(",  input_area , ")"
                            )
        } else {
            input_area <- input$select_neighbour %>%  
                paste0("'", ., "'") %>% 
                paste(collapse = ", ")
            
            query <- paste0("SELECT amenities FROM listing
                             WHERE neighbourhood_cleansed IN(",  input_area , ") AND room_type = '", input$select_room, "'"
                            )
        }
        
        out_db <- dbGetQuery(con1, query)
        
        
        list_amenities <- map(out_db$amenities, function(x) x %>% strsplit(", ") %>% unlist() ) %>% 
            unlist()
        
        df_amenities <- data.frame(amenities = list_amenities) %>% 
            count(amenities, name = "frequency") %>% 
            mutate(n_data = nrow(out_db),
                   ratio = frequency/nrow(out_db),
                   text_amenities = amenities %>% 
                       str_replace_all(" ", "\n")
                   )
        
        plot_ly(
            data = df_amenities,
            type = "treemap",
            labels = ~text_amenities,
            parents = "", 
            hovertemplate = paste0("<b>", df_amenities$amenities, "</b><br>",
                                   "Number of Listing with This Amenities: ", number(df_amenities$frequency, big.mark = ","), " (", percent(df_amenities$ratio, accuracy = 0.1), ")<br>",
                                   "<extra></extra>"
                                   ),
            values = ~frequency
            )  %>% 
            layout(title = "<b>Commonly Provided Amenities</b>") %>% 
            config(displayModeBar = F)
        
        
        
    })
```



Host 
=====================================  
Row {data-height=150}
-----------------------------------------------------------------------
### Airbnb Host Partner
Airbnb hosts are required to <a href=  https://www.airbnb.com/help/article/1237/verifying-your-identity target='_blank'> confirm their identity</a> such as their name, address, phone, etc.  <a href= https://www.airbnb.com/help/article/828/what-is-a-superhost target='_blank'>Superhosts</a> are experienced hosts 
who provide a shining example for other hosts, and extraordinary experiences for their guests.


<b>Total earning</b> gained by hosts are calculated by the total product of their <b>listing price</b>, 
                                                       <b>number of reviews </b> to represent the number of customers, and 
                                                       the <b> minimum night</b> to represent the number of night stays.
                                                       
Row {data-height=200}
-----------------------------------------------------------------------
### SUPERHOST
```{r}
renderValueBox({
  valueBox(value=number(n_superhost$frequency,big.mark=","),icon="fa-star",caption="Superhost", color="#FFCC99")
})
```

### VERIFIED HOST
```{r}
renderValueBox({
  valueBox(value=number(n_host_verified$frequency,big.mark=","),icon="fa-check",caption="Verified Host", color="#99FF99")
})
```

### UNVERIFIED HOST 
```{r}
renderValueBox({
  valueBox(value=number(n_host_non_verified$frequency,big.mark=","),icon="fa-times",caption="Unverified Host", color="#FF6666")
})
```

Row {.tabset data-height=600}
-----------------------------------------------------------------------

### Number of Host Joined Over Time
```{r}
plotlyOutput("host_join")

  # Host Join Timeline -----------
    output$host_join <- renderPlotly({
        
        query <- "SELECT MONTHNAME(host_since) as month, YEAR(host_since) as year,  COUNT(*) as frequency
        FROM host_info
        WHERE host_since IS NOT NULL
        GROUP BY month, year"
        
        out_db <- dbGetQuery(con1, query)
        
        p <- out_db %>% 
            mutate(date = paste0(year, "-", month, "-1") %>% 
                       ymd()
            ) %>% 
            pad(interval = "month",
                start_val = ymd( paste0(min(.$year), "-1-1") )
                ) %>% 
            mutate(month = month(date, label = T, abbr = F),
                   year = year(date)
                   ) %>% 
            replace_na(list(frequency = 0)) %>% 
            
            ggplot(aes(x = year,
                       y = month,
                       fill = frequency, 
                       text = glue("Year: {year}
                         Month: {month}
                         Number of Host Joined: {frequency}")
                       )
                   ) +
            geom_tile(color = "white") +
            scale_x_continuous(breaks = seq(2000, 2025, 2) ) +
            theme_pander() +
            scale_fill_viridis_c(option = "B") +
            labs(x = "Year",
                 y = NULL,
                 fill = "Frequency",
                 title = "Number of Host Joined Over Time")
        
        ggplotly(p, tooltip = "text") %>% 
            config(displayModeBar = F) 
        
    })


                                       
```

### Commonly Given Verification Identity
```{r}
plotlyOutput("host_verification")

# Commonly Identified Information -------------------------
    output$host_verification <- renderPlotly({
        
        out_db <- dbGetQuery(con1,
                           "SELECT host_id, host_name, host_verifications, host_identity_verified
                           FROM host_info
                           WHERE host_identity_verified IS NOT NULL AND host_verifications IS NOT NULL
                           "
        )
        
        
        out_db <- out_db %>% 
            mutate(host_verifications = tolower(host_verifications))
        
        list_verification <- map(out_db$host_verifications, function(x) x %>% strsplit(", ") %>% unlist() ) %>% 
            unlist() %>% str_remove_all('"')
        
        host_info_verify <- data.frame(verification = list_verification) %>% 
            count(verification, name = "frequency") %>% 
            mutate(n_data = nrow(out_db),
                   ratio = frequency/nrow(out_db),
                   verification = verification %>% 
                       str_replace_all("_", " ") %>% 
                       str_to_title(),
                   text_verification = verification %>% 
                       str_replace_all(" ", "\n")
                   )
        
        plot_ly(
            data = host_info_verify,
            type = "treemap",
            labels = ~text_verification,
            parents = "", 
            hovertemplate = paste0("<b>", host_info_verify$verification, "</b><br>",
                                   "Number of Host with This Identity Information: ", number(host_info_verify$frequency, big.mark = ","), " (", percent(host_info_verify$ratio, accuracy = 0.1), ")<br>",
                                   "<extra></extra>"
            ),
            values = ~frequency
        )  %>% 
            layout(title = "<b>Commonly Given Verification Identity</b>") %>% 
            config(displayModeBar = F)
        
        
    })


```

### Top 50 Host by Total Earning
````{r}
ui<-column(height=12,width=12, h2("Top 50 Host by Total Earning"),
checkboxInput(inputId = "select_superhost", label = "Include Superhost", value = T),
reactableOutput("host_top"))
                                              
                                       


server<- shinyServer(function(input, output,session) { output$host_top <- renderReactable({
    
    if (input$select_superhost == T) {
      
      out_db <- dbGetQuery(con1,"SELECT listing.host_id, host_info.host_name, host_info.host_since,  host_info.host_is_superhost, host_info.host_identity_verified, COUNT(*) as number_of_listing, SUM( price * number_of_reviews * minimum_nights ) as earning, host_info.host_url
                FROM listing
                LEFT JOIN host_info
                ON listing.host_id = host_info.host_id
                WHERE host_info.host_since IS NOT NULL
                GROUP BY listing.host_id, host_info.host_name, host_info.host_since, host_info.host_is_superhost, host_info.host_identity_verified, host_info.host_url
                ORDER BY earning DESC
                LIMIT 50")
    } else {
      
      out_db <- dbGetQuery(con1,"SELECT listing.host_id, host_info.host_name, host_info.host_since,  host_info.host_is_superhost, host_info.host_identity_verified, COUNT(*) as number_of_listing, SUM( price * number_of_reviews * minimum_nights ) as earning, host_info.host_url
                FROM listing
                LEFT JOIN host_info
                ON listing.host_id = host_info.host_id
                WHERE host_info.host_is_superhost = 0 AND host_info.host_since IS NOT NULL
                GROUP BY listing.host_id, host_info.host_name, host_info.host_since, host_info.host_is_superhost, host_info.host_identity_verified, host_info.host_url
                ORDER BY earning DESC
                LIMIT 50")
    }
    
    reactable(out_db, 
              striped = T, highlight = T,
              columns = list(host_id = colDef(name = "Host ID",),
                             host_name = colDef(name = "Host Name",
                                                cell = function(value, index){
                                                  url <- sprintf("%s", out_db[index, "host_url"])
                                                  tags$a(href = url, value)
                                                }
                             ),
                             host_since = colDef(name = "Host Since"),
                             number_of_listing = colDef(name = "Number of Listing", minWidth = 100,
                                                        style = list(fontFamily = "monospace")
                             ),
                             earning = colDef(name = "Total Earning", 
                                              format = colFormat(separators = T),
                                              style = list(fontFamily = "monospace")
                             ),
                             host_is_superhost = colDef(name = "Superhost",
                                                        minWidth = 100,
                                                        cell = function(value, index){
                                                          if (value == 0) "\u2718" else "\u2713"
                                                        }
                             ),
                             host_identity_verified = colDef(name = "Identity Verified",
                                                             minWidth = 100,
                                                             cell = function(value, index){
                                                               if (value == 0) "\u2718" else "\u2713"
                                                             }
                             ),
                             host_url = colDef(show = F)
              )
              
    )
    
  })})
shinyApp(ui,server)
```